Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-10-03 Ben_Manuscripts/Paper1/Outline.tex
added forcefield parameters to gaff
Outline updates

  (1) Do monomers partition into and persist as defined monomer layers?
  H\textsubscript{II} and Col\textsubscript{h} phase LC membrane pores are 
  thought to be composed of monomer layers stacked on top of each other. 
  \begin{itemize}
  	\item Their existence is supported by experimental evidence of strong 
	$\pi$-$\pi$ stacking interactions in the direction perpendicular to the
	membrane plane.
	\item $\pi$-$\pi$ stacking will only occur between monomer head groups which
	leaves no description of what is happening in monomer tail region
	\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
  \end{itemize}

  (2) If layers do exist, how many monomers constitute a single layer?
  There has been no definitive answer to the question in literature.
  \begin{itemize}
    \item A simple molecular simulation study of a similar molecule suggested
    that there are 4 monomers in each layer. Their estimation is based on a
    simulated system containing only 16 total monomers which likely does not sufficiently
    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
    \item A separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    \item A molecular model orders of magnitude larger than any other reported atomistic 
    liquid crystal membrane simulations has the best chance of directly answering this question.
  \end{itemize}

@@

  We chose the initial layer spacing based on R-$\pi$.
  \begin{itemize}  
    \item Each monomer was rotated so the plane of the aromatic head groups would
    be parallel to the xy plane.
    \item The layers are placed so aromatic rings are stacked 3.7 \angstrom~
    apart in the z-direction.
    \item We extracted the equilibrium distance between layers based on the first
    peak of a spatial correlation function, $g(z)$, measured along the z-axis (perpendicular to 
    the membrane plane)
    \item To calculate $g(z)$, we binned the z component distances between 
    the center of mass of each benzene ring and all others of the same pore 
    over 50 ns of equilibrated trajectory and then normalized by the average
    number density.
    \item Our simulations tend to equilibrate to a wider interlayer spacing of
    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
    spacings greater than 4 \angstrom~.
  \end{itemize}

@@

  To answer (1), we verified that the system stays partitioned into layers by
  plotting the pair correlation function calculated between aromatic rings along
  the length of the pores (Fig~\ref{fig:zdf}).
  % BJC: add how this calculation is done to methods section (put where I talk about
  % choosing distance between layers
  \begin{itemize}
	\item Period of fluctuation (layer spacing)
        \item Magnitude of fluctuations
	\item Comment on difference between offset/layered, number of monomers per layer
  \end{itemize}

@@

  To discern the composition of the monomer layers, addressing (2), we ran 
  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
  \begin{itemize}
  	\item Both the sandwiched and parallel displaced configurations were tested.
	\item All systems are stable after 400 ns of simulation.  % BJC: edited this for clarity
        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
	%BJC: Working on getting them all run out to 400 ns
	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
	\item Systems built with 5 monomers in each layer equilibrate to a pore spacing
	that is most consistent with the experimental value of 4.12 nm derived from
	SAXS measurements (Figure~\ref{fig:SAXS}).
	\item The remainder of this discussion will focus on the analysis of systems
	built with 5 monomers per layer. 
  \end{itemize}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{ccc}
  \toprule
  		   & \multicolumn{2}{c}{Starting Configuration} \\
  \hline
  Monomers per layer & Sandwiched & Parallel Displaced \\
  \midrule
  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
  \bottomrule
  \end{tabular}
  \caption{The pore spacing (given in $\nm$) of the model increases as
  number of monomers in each layer increases. The pore spacing of a system
  starting in the sandwiched configuration is systematically lower than 
  that started in an offset configuration. Systems built with 5 monomers
  per layer in a parallel displaced configuration result in a pore spacing
  closest to the experimental 4.12 $\nm$~}\label{table:p2p} 
  \end{table}

@@

  The $z$-direction correlation functions show that layers in our model prefer
  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration 
  with layers stacked 4.0 $\nm$ apart and to our surprise, we observed
  long-term stability of a qualitatively different configurations suggesting
  that we have found more than one metastable free energy basin.
  %that the initial distance between layers can influence the approach towards 
  %equilibrium.
  \begin{itemize}
  	\item Equilibrated systems built according to the 3.7 \angstrom~layer spacing 
        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore 
	structure.
        \item We will refer to this large set of configurations, with an open pore, as 
        the OP Basin (open pore) (Figure~\ref{fig:abasin}).
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom~ apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
	\item This will be called the CP Basin (closed pore) (Figure~\ref{fig:bbasin}).
	\item This LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Because the pore structure will vary between each Basin, understanding 
	which phase exists experimentally is necessary in order to ensure we are 
	studying the system which actually dominates.
  \end{itemize}

  \begin{figure}[!ht]
        \centering
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{280K_tramp_close.png}
                \caption{}\label{fig:abasin}
        \end{subfigure}
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{340K_tramp_close.png}
                \caption{}\label{fig:bbasin}
        \end{subfigure}
	\caption{From a qualitative standpoint, Basin A (a) is characterized by a
	hollow cylindrical pore while pores in Basin B (b) are characterized by a
	higher degree of radial disorder}\label{fig:basins}
  \end{figure}

@@

  We answer question (3) by simulating X-ray diffraction patterns produced from
  equilibrated MD trajectories. We leave open the possibility that the 
  experimental structure might be reminiscent of the parallel displaced or sandwiched
  configurations in the OP or CP basins.
  %We created systems using three distinct initial configurations and examined
  %their structure by simulating X-ray diffraction patterns produced from equilibrated MD trajectories.
  \begin{itemize}
  	\item OP Basin systems were built in both the parallel displaced and sandwiched 
	configurations with an intial layer spacing of 3.7 \angstrom~.
	\item A third system was created by stacking layers in the sandwiched 
	configuration 5 \angstrom~apart in order to guide it towards the CP Basin.
	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
	\item The three systems were equilibrated according to our procedure with
	NPT simulations of greater than 400 ns.
	\item Simulated diffration patterns were generated using portions of the
	trajectory after equilibration.  
	\item We assume the simulation has equilibrated when the distance between 
	pores and the membrane thickness stopped changing.
	\item Simulated diffraction patterns for all three structures are shown in 
	Figure ~\ref{fig:XRDsim}. 
  \end{itemize}

  % Three paragraphs instead here? Talk about disordered, parallel displaced and 
  % layered separately? Try it. 
  % Talk about disordered last so it leads in to 
  % Also maybe don't talk about question 4 until after this

  %Full comparison of experimental 2D WAXS with simulated X-ray diffraction
  %patterns shows the most consistency with the offset configuration in the OP basin.

@@

  The spots that appear in the simulated XRD pattern of the OP basin
  conformations are a result of the way alkane tails pack together.
  \begin{itemize}
  	\item Previously, the spots in the diffraction pattern had been explained 
	as the product of tilted alkane chains.
	\item We measured the tilt angle of the alkane chains and showed that our 
	system equilibrates to an average tilt angle close to zero degrees (See Supplemental Information). 
	\item To understand the origin of the spots, we determined which atoms gave rise to the feature
	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
        that the spots arise as a consequence of the tails. 
	\item By removing atoms from the trajectory and simulating a diffraction 
	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
	\item Since the tails stay nearly flat, we plotted the centroids of the 
	tails and measured the angle between each centroid and its nearest neighbors
	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
	\item The distribution of these angles is consistent with the location of 
	the spots (Figure~\ref{fig:tail_packing}).
	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
	of spots are located on the simulated patterns (See Supplemental Information for quantitative proof)
	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
        and found the angle at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which 
        is a reconcilable difference with our simulated results.  
  \end{itemize}

  \begin{figure}[ht]
  \centering
  \begin{subfigure}{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{offset_tail_packing.png}
        \caption{}~\label{fig:offset_tails}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{angles_traj_layered.png}
        \caption{}~\label{fig:layered_tails}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{integrated_WAXS_ring.png}
        \caption{}~\label{fig:rz_layered}
  \end{subfigure}
  \caption{The distribution of angles w.r.t. xy plane between alkane chain tail centroids and nearest
  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (b) configurations both show
  distinct peaks at $\pm$ 33 $\degree$. (c) Integrated 2D WAXS data between $q_r$=1 and $q_r$=1.42 shows
  distinct peaks at with maxima at $\pm$ 37 $\degree$}~\label{fig:tail_packing}
  \end{figure}

  %MRS: one could ask the question about basins for the parallel displaced and sandwich as well.  
  %MRS: we had talked a lot about interconversion (or conversion one way but not other?) but 
  %MRS: I think things have changed since then? 
  The disordered basin shares little in common with the ordered basin but 
  its long term stability suggests that it can exist under some conditions.  
  We observed that Basin B is the dominant configuration at higher temperatures.
  \begin{itemize}
        \item We linearly ramped the temperature of a system in Basin A
        from 280K to 340K over 100 ns.
        \item Visually, there is a distinct change in pore structure from one
        characteristic of Basin A (Figure~\ref{fig:280K_pore}) to one characteristic of
        Basin B (Figure~\ref{fig:340K_pore}).
        \item The slope of all order parameters changes between 315K and 325K
        (\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
        possibility of an abrupt change in system ordering.
        \item Our 100 ns temperature ramp was likely too fast and caused the system
        to suffer from hysteresis.
  \end{itemize}

  We can not immediately classify Basin A and Basin B as separate phases.
  \begin{itemize}
	\item To prove the existence of two phases we need evidence of a
	a first order phase transition.
	\item A first order phase transition can be denoted by a discontinuity
        of some order parameter in response to an external condition such as
	temperature.
	\item We chose three easily measurable order parameters: the distance
	between pores, the membrane thickness and the ratio of pore radius to
	the uncertainty in pore radius.  % BJC: these may change
        \item The pore radius is divided by its uncertainty as a way of quantifying
        the degree to which monomers obstruct the pore region.
  \end{itemize}

@@

  \begin{figure}[!ht]
        \centering
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                % these next 2 figures are REALLY big (12-18M). Likely could reduce to near 0.5-1.0 MB without loss of 
                % necessary resolution.  A few other figures could have resolution reduced.
                \includegraphics[width=\textwidth]{280K_tramp_close.png}
                \caption{}\label{fig:280K_pore}
        \end{subfigure}
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{340K_tramp_close.png}
                \caption{}\label{fig:340K_pore}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.325\textwidth}
                \centering
                \includegraphics[width=\textwidth]{p2p_tramp.png}
                \caption{}\label{fig:p2p_tramp}
        \end{subfigure}
        \begin{subfigure}[b]{0.325\textwidth}
                \centering
                \includegraphics[width=\textwidth]{thickness_tramp.png}

                \caption{}\label{fig:thickness_tramp}
        \end{subfigure}
        \begin{subfigure}[b]{0.325\textwidth}
                \centering
                \includegraphics[width=\textwidth]{order_tramp.png}
                \caption{}\label{fig:order_tramp}
        \end{subfigure}
        \caption{(a) The open pore structure exhibited by a structure equilibrated
        at 280K is characteristic of Basin A. (b) The closed pore structure with
        a high degree of radial disorder exhibited when the structure in (a) is
        heated to 340K is characteristic of Basin B. (c) A plot of distance between pores
        vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs.
        temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
        its uncertainty changes slope near 315K.}\label{fig:tramp}
  \end{figure}

>>>>

%BJC: How question (1) and (2) used to be ordered:
%
%  (1) Do monomers partition into and persist as defined monomer layers?
%  H\textsubscript{II} and Col\textsubscript{h} phase LC membrane pores are 
%  thought to be composed of monomer layers stacked on top of each other. 
%  \begin{itemize}
%  	\item Their existence is supported by experimental evidence of strong 
%	$\pi$-$\pi$ stacking interactions in the direction perpendicular to the
%	membrane plane.
%	\item $\pi$-$\pi$ stacking will only occur between monomer head groups which
%	leaves no description of what is happening in monomer tail region
%	\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
%	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
%  \end{itemize}
%
%  (2) If layers do exist, how many monomers constitute a single layer?
%  There has been no definitive answer to the question in literature.
%  \begin{itemize}
%    \item A simple molecular simulation study of a similar molecule suggested
%    that there are 4 monomers in each layer. Their estimation is based on a
%    simulated system containing only 16 total monomers which likely does not sufficiently
%    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
%    \item A separate calculation based on the volume of the liquid crystal monomers proposes
%    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
%    \item A molecular model orders of magnitude larger than any other reported atomistic 
%    liquid crystal membrane simulations has the best chance of directly answering this question.
%  \end{itemize}

  Monomers in the Col\textsubscript{h} system are theorized to be partitioned
  into stacked layers which form columnar pores. There has been no definitive
  answer in literature regarding the number of monomers in each layer. We want to
  know (1) If layers do exist, how many monomers constitute a single layer?
  \begin{itemize}
    \item A simple molecular simulation study of a similar molecule suggested
    that there are 4 monomers in each layer. Their estimation is based on a
    simulated system containing only 16 total monomers which likely does not sufficiently
    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
    \item A separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    \item A molecular model orders of magnitude larger than any other reported atomistic 
    liquid crystal membrane simulations has the best chance of directly answering this question.
    \item We can directly change the layer composition and note its effect on membrane structure.
  \end{itemize}

  (2) Does our model support the existence of layers and if so, how well defined
  are the layers?
  \begin{itemize}
       \item Experimentally, their existence is supported by evidence of strong 
       $\pi$-$\pi$ stacking interactions in the direction perpendicular to the
       membrane plane.
       \item $\pi$-$\pi$ stacking will only occur between monomer head groups which
       leaves no description of what is happening in the monomer tail region
       \item The tails may entangle isotropically while stacking order is maintained
       among headgroups. 
       %\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
       %with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
  \end{itemize}

@@

  We chose the initial layer spacing based on R-$\pi$.
  \begin{itemize}  
    \item Each monomer was rotated so the plane of the aromatic head groups would
    be parallel to the xy plane.
    \item The layers are placed so aromatic rings are stacked 3.7 \angstrom~
    apart in the z-direction.
    \item We extracted the equilibrium distance between layers based on the first
    peak of a spatial correlation function, $g(z)$, measured along the z-axis (perpendicular to 
    the membrane plane)
    \item To calculate $g(z)$, we binned the z component distances between 
    the center of mass of each benzene ring and all others of the same pore 
    over 50 ns of equilibrated trajectory and then normalized by the average
    number density.
    \item To extract the average distance between layers we applied a discrete 
    fourier transform to the data and extracted the highest intensity frequency 
    \item We compare the degree of layering between systems based on the 
    amplitude of the first peak in $g(z)$. We halve the difference between the 
    maximum of the first peak and the following minimum. We compare the difference
    to the mean to get a percentage deviation from the average number density.
    \item Our simulations tend to equilibrate to a wider interlayer spacing of
    $\approx$ 4.1 \angstrom~, which inspired separate systems starting with layer 
    spacings greater than 4 \angstrom~.
  \end{itemize}

@@

% BJC: How this section (||||) used to be ordered until deciding to put monomers / layer first
%                        VVVV
  %To answer (1), we verified that the system stays partitioned into layers by
  %plotting the pair correlation function calculated between aromatic rings along
  %the length of the pores (Fig~\ref{fig:zdf}).
  % BJC: add how this calculation is done to methods section (put where I talk about
  % choosing distance between layers
  %\begin{itemize}
%	\item Period of fluctuation (layer spacing)
 %       \item Magnitude of fluctuations
%	\item Comment on difference between offset/layered, number of monomers per layer
 % \end{itemize}

  % BJC: might replace with a figure containing alllllll of the zdf's
  %\begin{figure}[!ht]
%       \centering
%       \begin{subfigure}{0.45\textwidth}
%               \centering
%               \includegraphics[width=\textwidth]{zdf5layered.png}
%               \caption{}\label{fig:zdf_layered}
%       \end{subfigure}
%       \begin{subfigure}{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{zdf5offset.png}
%                \caption{}\label{fig:zdf_offset}
%        \end{subfigure}
%        \caption{Pair distribution functions of aromatic carbons for the
%        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
%        parallel displaced configurations. Clear periodic maxima in the 
%        $z$ probability density indicate distinct layers. The magnitude 
%        of the spikes with respect to the average suggest that the 5 
%        monomer per layer, sandwiched configuration possesses a higher 
%        degree of layer partitioning.}\label{fig:zdf}
%  \end{figure}

%  To discern the composition of the monomer layers, addressing (2), we ran 
%  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
  %\begin{itemize}
%  	\item Both the sandwiched and parallel displaced configurations were tested.
%	\item All systems are stable after 400 ns of simulation.  % BJC: edited this for clarity
        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
	%BJC: Working on getting them all run out to 400 ns
%	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
%	\item Systems built with 5 monomers in each layer equilibrate to a pore spacing
%	that is most consistent with the experimental value of 4.12 nm derived from
%	SAXS measurements (Figure~\ref{fig:SAXS}).
%	\item The remainder of this discussion will focus on the analysis of systems
%	built with 5 monomers per layer. 
%  \end{itemize}

  To discern the composition of the monomer layers, addressing (1), we ran
  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
  \begin{itemize}
        \item Both the sandwiched and parallel displaced configurations were tested.
        \item All systems are stable after 400 ns of simulation.  % BJC: edited this for clarity
        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
        %BJC: Working on getting them all run out to 400 ns
        \item Table ~\ref{table:p2p} shows the pore spacing for all systems tested.
        \item Systems built with 5 monomers in each layer equilibrate to a pore spacing
        that is most consistent with the experimental value of 4.12 nm derived from
        SAXS measurements (Figure~\ref{fig:SAXS}).
        \item The remainder of this discussion will focus on the analysis of systems
        built with 5 monomers per layer.
  \end{itemize}

  To answer (2), we verified that the system stays partitioned into layers by
  plotting the pair correlation function, $g(z)$ calculated between aromatic rings along
  the length of the pores (Fig~\ref{fig:zdf}).
  \begin{itemize}
        \item Sandwiched configuration layers stack 4.29 \angstrom apart while
        parallel displaced configuration layers stack 4.37 \angstrom apart.
        The power spectrums used to calculate the reported layer spacing are given in the 
        Supplemental Information.
	\item Even though the layer spacing is similar, the sandwiched configuration
	exhibits more defined layers with its first peak deviating from the mean 
        number density by 61 \%.
	\item The parallel displaced configuration deviates from the mean by only 
	12 \% in comparison.
  \end{itemize}

@@

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{ccc}
  \toprule
  		   & \multicolumn{2}{c}{Starting Configuration} \\
  \hline
  Monomers per layer & Sandwiched & Parallel Displaced \\
  \midrule
  4 & $3.71 \pm 0.04$ & $3.84 \pm 0.02$ \\
  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
  \bottomrule
  \end{tabular}
  \caption{The pore spacing (given in nm) of the model increases as
  number of monomers in each layer increases. The pore spacing of a system
  starting in the sandwiched configuration is systematically lower than 
  that started in an offset configuration. Systems built with 5 monomers
  per layer in a parallel displaced configuration result in a pore spacing
  closest to the experimental 4.12 nm}
  \label{table:p2p} 
  \end{table}

@@

  The $z$-direction correlation functions show that layers in our model prefer
  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration 
  with layers stacked 4.0 nm apart and to our surprise, we observed
  long-term stability of a qualitatively different configurations suggesting
  that we have found more than one metastable free energy basin.
  %that the initial distance between layers can influence the approach towards 
  %equilibrium.
  \begin{itemize}
  	\item Equilibrated systems built according to the 3.7 \angstrom~layer spacing 
        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore 
	structure.
        \item We will refer to this large set of configurations, with an open pore, as 
        the OP Basin (open pore) (Figure~\ref{fig:OPbasin}).
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom~ apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
	\item This will be called the CP Basin (closed pore) (Figure~\ref{fig:CPbasin}).
	\item This LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Because the pore structure will vary between each Basin, understanding 
	which phase exists experimentally is necessary in order to ensure we are 
	studying the system which actually dominates.
  \end{itemize}

  \begin{figure}[!ht]
        \centering
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{280K_tramp_close.png}
                \caption{}\label{fig:OPbasin}
        \end{subfigure}
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
                \caption{}\label{fig:CPbasin}
        \end{subfigure}
	\caption{From a qualitative standpoint, the OP Basin (a) is characterized by a
	hollow cylindrical pore while pores in the CP Basin (b) are characterized by a
	higher degree of radial disorder}\label{fig:basins}
  \end{figure}

@@

  We answer question (3) by simulating X-ray diffraction patterns produced from
  equilibrated MD trajectories. We leave open the possibility that the 
  experimental structure might be reminiscent of the parallel displaced or sandwiched
  configuration in the OP or CP basin.
  %We created systems using three distinct initial configurations and examined
  %their structure by simulating X-ray diffraction patterns produced from equilibrated MD trajectories.
  \begin{itemize}
  	\item OP Basin systems were built in both the parallel displaced and sandwiched 
	configurations with an intial layer spacing of 3.7 \angstrom~.
	\item A third system was created by stacking layers in the sandwiched 
	configuration 5 \angstrom~apart in order to guide it towards the CP Basin.
	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
	\item The three systems were equilibrated according to our procedure with
	NPT simulations of greater than 400 ns.
	\item Simulated diffration patterns were generated using portions of the
	trajectory after equilibration.  
	\item We assume the simulation has equilibrated when the distance between 
	pores and the membrane thickness stopped changing.
	\item Simulated diffraction patterns for all three structures are shown in 
	Figure ~\ref{fig:XRDsim}. 
  \end{itemize}

  %BJC: below (commented out) thesis is from when I had the following three paragraphs combined
  %Full comparison of experimental 2D WAXS with simulated X-ray diffraction
  %patterns shows the most consistency with the offset configuration in the OP basin.

@@

  R-spots appearing in the simulated XRD pattern of the OP basin
  conformations are a result of the way alkane tails pack together.
  \begin{itemize}
  	\item Previously, the spots in the diffraction pattern had been explained 
	as the product of tilted alkane chains. % BJC: reference
	\item We measured the tilt angle of the alkane chains and showed that our 
	system equilibrates to an average tilt angle close to zero degrees (See Supplemental Information). 
	\item To understand the origin of the spots, we determined which atoms gave rise to the feature
	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
        that the spots arise as a consequence of the tails. 
	\item By removing atoms from the trajectory and simulating a diffraction 
	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails}).
	\item Since the tails stay nearly flat, we plotted the centroids of the 
	tails and measured the angle between each centroid and its nearest neighbors
	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
	\item The distribution of these angles is consistent with the location of 
	the spots (Figure~\ref{fig:tail_packing}).
	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
	of spots are located on the simulated patterns (See Supplemental Information for quantitative proof)
	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
        and found the angle at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which 
        is a reconcilable difference with our simulated results.  
  \end{itemize}

  \begin{figure}
	\centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
		\caption{}\label{fig:topdown_tails_only}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{tails_rzplot.png}
		\caption{}\label{fig:tails_rzplot}
	\end{subfigure}
	\caption{(a) All atoms except carbon atoms making up the tails are removed from the 
	trajectory. (b) The simulated diffraction pattern of the tail-only trajectory still 
        shows R-spots}\label{fig:tails}
  \end{figure}

  \begin{figure}[ht]
  \centering
  	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
        		\centering
        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
        		\caption{}~\label{fig:offset_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
		\centering
	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
		        \caption{}~\label{fig:layered_tails}
		\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
	        \centering
		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
		        \caption{}~\label{fig:rz_layered}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
        	\centering
		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
		        \caption{}~\label{fig:test}
		\end{subfigure}
	\end{subfigure}
  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
  same peaks are visible when the 2D simulated diffraction data is radially integrate in the R-alkanes region,
  (b) and (d) respectively.}~\label{fig:tail_packing}
  \end{figure}

  %BJC: old version of above figure v v v
  %\begin{figure}[ht]
  %\centering

  %\begin{subfigure}{0.3\linewidth}
  %      \centering
  %      \includegraphics[width=\linewidth]{offset_tail_packing.png}
  %      \caption{}~\label{fig:offset_tails}
  %\end{subfigure}
  %\begin{subfigure}{0.3\linewidth}
  %      \centering
  %      \includegraphics[width=\linewidth]{angles_traj_layered.png}
  %      \caption{}~\label{fig:layered_tails}
  %\end{subfigure}
  %\begin{subfigure}{0.3\linewidth}
  %      \centering
  %      \includegraphics[width=\linewidth]{integrated_WAXS_ring.png}
  %      \caption{}~\label{fig:rz_layered}
  %\end{subfigure}
  %\caption{The distribution of angles w.r.t. xy plane between alkane chain tail centroids and nearest
  %neighbor centroids for equilibrated parallel displaced (a) and sandwiched (b) configurations both show
  %distinct peaks at $\pm$ 33 $\degree$. (c) Integrated 2D WAXS data between $q_r$=1 and $q_r$=1.42 shows
  %distinct peaks at with maxima at $\pm$ 37 $\degree$}~\label{fig:tail_packing}
  %\end{figure}

  The disordered basin shares little in common with the ordered basin but 
  its long term stability suggests that it can exist under some conditions.  
  We observed that Basin B is the dominant configuration at higher temperatures.
  \begin{itemize}
        \item We linearly ramped the temperature of a system in Basin A
        from 280K to 340K (just below the experimental isotropic transition temperature) over 100 ns.
        \item Visually, there is a distinct change in pore structure from one
        characteristic of the OP Basin (Figure~\ref{fig:280K_pore}) to one characteristic of
        the CP Basin (Figure~\ref{fig:340K_pore}).
        \item The slope of all order parameters changes between 315K and 325K
        (\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the
        possibility of an abrupt change in system ordering.
        \item Our 100 ns temperature ramp was likely too fast and caused the system
        to suffer from hysteresis.
  \end{itemize}

  We can not immediately classify the OP Basin and the CP Basin as separate phases.
  \begin{itemize}
	\item To prove the existence of two phases we need evidence of a
	a first order phase transition.
	\item A first order phase transition can be denoted by a discontinuity
        of some order parameter in response to an external condition such as
	temperature.
	\item We chose three easily measurable order parameters: the distance
	between pores, the membrane thickness and the ratio of pore radius to
	the uncertainty in pore radius.  % BJC: these may change
        \item The pore radius is divided by its uncertainty as a way of quantifying
        the degree to which monomers obstruct the pore region.
  \end{itemize}

@@

  \begin{figure}[!ht]
        \centering
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{280K_tramp_close.png}
                \caption{}\label{fig:280K_pore}
        \end{subfigure}
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{340K_tramp_close_full.png}
                \caption{}\label{fig:340K_pore}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.325\textwidth}
                \centering
                \includegraphics[width=\textwidth]{p2p_tramp.png}
                \caption{}\label{fig:p2p_tramp}
        \end{subfigure}
        \begin{subfigure}[b]{0.325\textwidth}
                \centering
                \includegraphics[width=\textwidth]{thickness_tramp.png}

                \caption{}\label{fig:thickness_tramp}
        \end{subfigure}
        \begin{subfigure}[b]{0.325\textwidth}
                \centering
                \includegraphics[width=\textwidth]{order_tramp.png}
                \caption{}\label{fig:order_tramp}
        \end{subfigure}
        \caption{(a) The open pore structure exhibited by a structure equilibrated
        at 280K is characteristic of the OP Basin. (b) The closed pore structure with
        a high degree of radial disorder exhibited when the structure in (a) is
        heated to 340K is characteristic of the CP Basin. (c) A plot of distance between pores
        vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs.
        temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
        its uncertainty changes slope near 315K.}\label{fig:tramp}
  \end{figure}
